Ion pairing controls rheological properties of polyelectrolyte crocodile line hydrogels

### 2016-01-11 PALSE/ion_pairing_paper.tex
Last paragraph of the intro. Plan and introduce crocodile line.

In the present report, we show that the mechanical/rheological properties of such smart hydrogels can be tuned to an extremely large extent by playing with the nature (hardness/softness) of the cationic repeating unit and the ion-paring strength of the associated counterion (\ce{F-}/\ce{Cl-}/\ce{Br-}/\ce{I-}). The viscoelastic and diffusion properties of the resulting materials are characterized by different rheological and calorimetric analyses, evidencing a strengthening of the gel network upon reinforcing the hard character of the cation and the soft character of the anionic counterion.

@@

\subsection{Crocodile chain model}

\begin{figure}
\includegraphics{dissociation.pdf}
\caption{Crocodile-line model. (a) Sketch of the network in the case of a crocodile line of size $n=3$ between cross-links (gray disks) and a persistence length $r_\mathrm{src}\approx 3D$. Empty circles are not individual monomers but electrostatic blobs of size $D$. Electrostatic blobs containing an anionic head are shown as black filled circles. (b) Relation between the number of monomers between uncondensed charges and the number of chains between cross-link points. The line corresponds to $n = A^2$.}
\label{fig:dissociation}
\end{figure}

>>>>

In the present report, we investigate the role of the dissociation rate of the poly(cationic) body on the mechanical/rheological properties of the hydrogel. In a first part we describe how we take advantage of our well-controlled synthesis to play systematically with the nature (hardness/softness) of the cationic repeating unit and the ion-paring strength of the associated counterion (\ce{F-}/\ce{Cl-}/\ce{Br-}/\ce{I-}). In a second part, we show the qualitative and quantitative variations of mechanical properties of the aqueous dispersion obtained from these well-characterized polymers. In a third part, we develop a microscopic model based on the idea that at low dissociation rates, cross-links are not separated by a single macromolecule but by several (up to hundreds) polymers in a supramolecular crocodile line. Finally, we discuss our results and possible applications of such smart hydrogels.

@@

\subsection{Crocodile line model}

\begin{figure}
\includegraphics{dissociation.pdf}
\caption{Crocodile line model. (a) Sketch of the network in the case of a crocodile line of size $n=3$ between cross-links (gray disks) and a persistence length $r_\mathrm{src}\approx 3D$. Empty circles are not individual monomers but electrostatic blobs of size $D$. Electrostatic blobs containing an anionic head are shown as black filled circles. (b) Relation between the number of monomers between uncondensed charges and the number of chains between cross-link points. The line corresponds to $n = A^2$.}
\label{fig:dissociation}
\end{figure}
